---
title: "HW0" 
format: html 
editor: visual
---

# Max Melnikas

## Problem 1

This is the well-known quadratic equation: $f(x) = ax^2 + bx + c = 0$

It can be solved through a series of steps, the first of which is finding the determinant: $D=\sqrt{b^2 - 4ac}$

If $b^2 - 4ac$ is less than zero, the equation has no real roots. If $b^2 - 4ac$ is equal to zero, the equation will have exactly one real solution. Finally, if $b^2 - 4ac$ is greater than zero, the equation will have two real solutions

```{r}
#| echo: false 
#| label: Determinant Calculation

a = 1 
b = 3 
c = 2 

# Determinant calculation using quadratic formula 
D = b ^ 2 - 4 * a * c 
cat("Determinant:",D)
```

The solutions to the equation follow the following formula: $$x_{1,2} = \frac{-b\pm\sqrt{b^2-4ac}}{2a}$$

```{r}
#| label: calculate roots 
#| echo: false 
if (D>0) { 
  x1 = (- b + sqrt(b^2 - 4 * a * c))/(2 * a) 
  x2 = (- b - sqrt(b^2 - 4 * a * c))/(2 * a) 
  cat("x1:",x1,"; x2:",x2) 
  } else if (D==0) { 
  x = (- b)/(2 * a) 
  cat("x1 = x2 =",x) 
  } else print("There are no real roots")
```

```{r}
#| label: graphing 
#| echo: false 
x <- seq(-5, 5, length = 300) 
plot(x, a*x^2 + b*x + c, type = "l") 
abline(h = 0, lty = 2)
```
